\vspace{-0.25em}\thetitle

### 2009-07-17 paper.tex
...

\newfootnote{\flownote}{We use the common definition of a \textit{flow} as a sequence of packets sharing the same  ``5-tuple'': \caps{IP} protocol type, source and destination nodes, and \caps{TCP/UDP} port numbers.}

@@

At this point it may be wise to address what we mean by prediction.
Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
flow behavior is nondeterministic---flows may exhibit the same initial behavior but subsequently behave quite differently.
The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.

>>>>

\newfootnote{\flownote}{We use the common definition of a \textit{flow} as a sequence of packets sharing the same  ``5-tuple'': IP protocol type, source and destination nodes, and TCP/UDP port numbers.}

@@

At this point it may be wise to address what we mean by prediction.
Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
flow behavior is nondeterministic---flows may exhibit the same initial behavior but subsequently behave quite differently.
The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.
When compared with a specific outcome, such a prediction cannot be said to be ``wrong or right.''
How then can one measure the quality of a predicted distribution of outcomes?
This is a subtle and difficult issue is central to our evaluation methodology.
